Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-05-24 RNARedPrint-Bioinfo2018.tex
Edit caption of new results figure

\begin{figure}
  {\includegraphics[width=\linewidth,trim={.2cm .3cm .2cm 5cm},clip]{Figs/statistics-overall}}
  \caption{Comparison of the \Obj{}
  (see Eq.~\eqref{eq:blueprintobjective}; smaller values $\to$ better designs) for sequences sampled by
  \ourprog{} and uniform sampling (\RNAblueprint) for six benchmark sets. For both sampling scheme, resulting sequences are either directly reported, or futher optimized using a local search heuristics.}
\label{fig:benchmark-results}
\end{figure}

>>>>

\begin{figure}
  {\includegraphics[width=\linewidth,trim={.2cm .3cm .2cm 5cm},clip]{Figs/statistics-overall}}
  \caption{Comparison of the \Obj{} (see
    Eq.~\eqref{eq:blueprintobjective}; smaller values $\to$ better
    designs) for sequences sampled by \ourprog{} and uniform sampling
    (\RNAblueprint) for six benchmark sets. For both sampling schemes,
    we show the MultiDefects of the sampled sequences, as well as
    results after further optimization by local search (``+ Opt.'').}
\label{fig:benchmark-results}
\end{figure}
